The evolution of gene expression in the term placenta of viviparous mammals

### 2016-03-22 manuscript/manuscript.Rnw
fix lineage typo

\begin{table}
  \footnotesize
<<human.lineage.specific,echo=FALSE,results="asis">>=
hum.all.lin.spec <-
    placenta.lineage.specific.table("hum.all",
                                    lineage.table=human.mouse.linage.specific.analysis,
                                    members=40)
setkey(hum.all.lin.spec,"Human Symbol")
@ 
\caption{Genes whose expression changed significantly in \human
  as compared to all other analyzed species.}
\label{tab:human_lineage_specific}
\end{table}

>>>>

\begin{table}
  \footnotesize
<<human.lineage.specific,echo=FALSE,results="asis">>=
hum.all.lin.spec <-
    placenta.lineage.specific.table("hum.all",
                                    lineage.table=human.mouse.lineage.specific.analysis,
                                    members=40)
setkey(hum.all.lin.spec,"Human Symbol")
@ 
\caption{Genes whose expression changed significantly in \human
  as compared to all other analyzed species.}
\label{tab:human_lineage_specific}
\end{table}
